Automatic Visual Inference for Linear Regression

### 2022-03-15 Milestone_presentation_1/Milestone_presentation_1/Milestone_presentation_1.Rmd
finish heter

>>>>

#### The **effect size** is derived as $ES = b\sqrt{n}$.

.pull-left[
```{r}
mod <- heter_model(a = -1, b = 30)
mod$plot_lineup(mod$gen_lineup(300), remove_grid_line = TRUE, theme = theme_light()) + xlab("Fitted values") + ylab("Residuals")
```

.caption[
Fig. 10: _A lineup of residual plots generated with the heteroskedasticity model._ 
]
]

.pull-right[

```{r}
set.seed(10086)
mod <- heter_model(0, 1)
mod$plot(mod$gen(500, fit_model = TRUE), size = 1, theme = theme_light(base_size = 10)) + ggtitle(glue::glue("Effect size: {round(mod$effect_size(mod$gen(500)),2)}")) + xlab("Fitted values") + ylab("Residuals") -> p1
mod <- heter_model(0, 3)
mod$plot(mod$gen(500, fit_model = TRUE), size = 1, theme = theme_light(base_size = 10)) + ggtitle(glue::glue("Effect size: {round(mod$effect_size(mod$gen(500)),2)}")) + xlab("Fitted values") + ylab("Residuals") -> p2
mod <- heter_model(0, 9)
mod$plot(mod$gen(500, fit_model = TRUE), size = 1, theme = theme_light(base_size = 10)) + ggtitle(glue::glue("Effect size: {round(mod$effect_size(mod$gen(500)),2)}")) + xlab("Fitted values") + ylab("Residuals") -> p3
mod <- heter_model(0, 81)
mod$plot(mod$gen(500, fit_model = TRUE), size = 1, theme = theme_light(base_size = 10)) + ggtitle(glue::glue("Effect size: {round(mod$effect_size(mod$gen(500)),2)}")) + xlab("Fitted values") + ylab("Residuals") -> p4

.caption[
Fig. 11: _Residual plots of heteroskedasticity model under different effect sizes._ 
]
